Molecular dynamics simulation of synchronization in driven particles

### 2021-02-03 manuscript/manuscript_ajp_2020.tex
added parameters figs

%In Fig.~\ref{fig:0} 
The driven particle adjusts
its motion to traverse
the periodic landscape with the same rhythm as 
the applied time-dependent force $F^d(t)$.
When $F^d(t) > A_p$, a particle can 
overcome the barrier height of the landscape,
and 
the particle hops between minima in the energy landscape.
%
In Fig.~\ref{fig:0}(a)
we plot $F^d(t)$ %defined in Eq.~\ref{eq:drive}.
as a function of time with
%The time independent
constants $F^{dc}=0.1$, 
$F^{ac}=0.05$ and $f=0.01$ cycles per time unit $\tau$.
The temporal period of the driving force is
$T = 1/f = 100 \tau$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%RAMP
%To avoid transient oscillations at early times, the dc driving force is initially zero and slowly increased %$F^{dc}$. at a rate of $\Delta F^{dc} = 0.01$ every $\Delta t = 4$ time units  to the constant value $F^{dc}=0.1$. In Fig.~\ref{fig:0}(a) we plot $F^{dc}$ in blue to show the increase in  $F^{dc}$ for the first $40$ time units In orange we show  the combined ac and dc drive $F^d(t)$ when the magnitude of the ac applied force is initially zero.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%since $\sin{(0)}=0$.
We mark the maxima of $F^{ac}(t)$
with the
vertical dashed lines %in panels (a) and (b)
-- i.e. $\sin{(\omega t)} = 1$.
%
%
%with the initial driving force at is minimum value 
%$F^d(0) = F^{dc}$. 
%
In Fig.~\ref{fig:0}(b) 
we show the $y-$position of the particle
as a function of time.
We 
normalize $y$ by $\lambda$ %, the spatial period of the potential
to show  particle motion between substrate minima.  
The initial particle position is $y = 0 $. %1 a_0$,
%where the $F^l$ is negative.
%JUST BECAUSE
%causing the particle to move to
%a landscape minima at the start of the simulation.
As the driving force increases,
%the effects of the landscape become less obvious,
the motion of the particle
synchronizes with the driving period $T$.
We measure 
average particle velocity $\langle{v}_y\rangle$
as the average displacement %$\Delta y = y(t_0+T) - y(t_0)$
over the period of the driving force.
The particle moves
in the positive y-direction
through $\Delta y = 2 \lambda$ over the time period $T$,
with 
the average velocity 
$\langle {v}_y \rangle= 2 \lambda f$. % where $T = 1/f$.
The horizontal dashed lines
coincide with %the condition the is
minimum substrate force  $F^l = -A_p$,  
i.e. $\sin{(\pi y / \lambda)} = 1$.
%or $\pi y / \lambda = m \pi/2$, where $m = 1, 5, 7$, {\it etc.}
%Once the particle motion
%coincides with the applied drive,
%indicating synchronization,
The particle synchronizes its motion such that the 
driving force is maximum when the landscape 
force is minimum,
as indicated with %the coincidence of 
with the intersection of
horizontal and vertical lines
and the particle position $y$.
The slope of $y/\lambda$
is proportional to the net force on the particle.
This can be seen in 
Fig.~\ref{fig:0} %we demonstrate this relationship,
where local extrema appear in $y/\lambda$
when $F_{D}(t) \approx 0 $.

@@

  Newton's second law states that
  the acceleration of a particle $i$
  is proportional to 
  the sum of forces on the particle 
  \begin{equation}
  m_i \vec{a}_i = \sum \vec{F}_i
  \label{eq:n2l}
  \end{equation}
  where the constant of proportionality is the
  inertial mass $m_i$.  
  The addition of a dissipative force to a dynamical equation 
  of colloid motion 
  is typically modeled
  with a drag force proportional to the particle's velocity
  in the opposite direction of motion 
  $\vec{F}^{drag} = - \gamma \vec{v}_i$
  where $\gamma = 3 \pi \eta D$ is the drag coefficient
  described in Ex.~\ref{ex:reynolds}.
  The ratio of $m/\gamma$ is %has units of time, % and is 
  known as the momentum relaxation time, %.
  and is small for
  particles with low Reynolds numbers.
  The mass of the
  typical experimental colloid particle is $15$ picograms,
  leading to a momentum relaxation time
  % \tau = 15 nanograms/(3 pi D \eta)
  %$15*10^-12 / (3pi * 3*10^-6 meters * 0.001 Pa-s * 1000 g/kg)$  %1 Pa-s = 1 N s /m^2 = 1 kg /(m s)
  on the order of microseconds.
  %of $1.6 ~\mu$s.
  Confirm for the values listed in Table ~\ref{tab:1},
  the momentum relaxation time is 
  $m/\gamma = 0.5 ~\mu$s.

@@

  When solving ordinary differential equations,
  the Euler method is effective for solving linear equations
  of the form
  $dy/dt = f(t,y(t))$ with initial condition $y(t_0) = y_0$.
  The solution is calculated algorithmically
  by stepping in time through $n$ integer steps
  $t_n = t_0 + n \Delta t$.
  At each subsequent step the new
  value for $y$ is calculated as a map solution using
  discrete times 
  $y_{n+1} = y_n + f(t_n,y_n)$.
  The Euler method can be applied to non-linear
  equations effectively if the time step $\Delta t$
  is kept sufficiently small \cite{Newman}.
  In our simulations we use the timestep $\Delta t = 0.001$,
  but we find for a single particle
  we can just as easily used 
  %examine 
  %for
  timesteps $\Delta t = 0.01$ and $\Delta t = 0.1$
  over the same maximum time
  (i.e. decrease the overall simulation time and sampling rate)
  and reproduce the motions shown in Fig.~\ref{fig:0}(b).
  This is due to the linear nature of the solution,
  and the lack of interaction with neighboring particles.
  Apply the Euler method to our equation
  of motion to solve for the analytic expression
  of position of a particle
  $y_n$ at the $nth$ timestep (i.e. Eq.~\ref{eq:euler}).
  %How to the motions of the particle compare when the timestep
  %becomes large?

  {\it small timesteps matter a great deal when particle interactions
    are included in the model.  I have demonstrated that
    without particle interactions we can increase the timestep
  with no penalty, so this isn't a very interesting problem.}

  %FOLLOW UP WITH THIS!
  %Because we are performing molecular dynamics
  %for a single particle on a smooth potential energy landscape,
  %we use a large simulation time step of 
  %$\Delta t = 0.01$.  %In Sec.~\ref{sec:sync},
  %we decrease the time step
  %to treat multiple particle interactions.

@@

  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{brownian_particle_dt0.1}.pdf}
      \caption{
        Motion of a particle undergoing Brownian motion
        on a washboard potential
        energy landscape.
        (a) $T/A_p = 4.0$ no hopping occurs.
        (b) $T/A_p = 5.0$ a single hop occurs at $t = 130000$
        (c) $T/A_p = 6.0$ many hops occur.
        Note the scale of the $y-$axis differs in each panel.
      }
      \label{fig:brownian}
    \end{figure}
  \end{center}
  In Fig.~\ref{fig:brownian}
  we show the position versus time of a simple particle
  confined to a sinusoidal landscape
  undergoing Brownian motion.
  We increase the temperature relative
  to the amplitude of the landscape
  troughs until the particle enters a hopping regime.
  In  Fig.~\ref{fig:brownian}(a)
  $T/A_p = 4.0$ and the particle executes a 
  random walk centered at the potential minima $y/\lambda = 10$.
  We ran many simulations and never observed a hop to another minima.
  In  Fig.~\ref{fig:brownian}(b)
  $T/A_p = 5.0$ where hops between
  potential minima are possible but not probable,
  a single hop occurs from
  $y/\lambda = 10$ to $y/\lambda = 11$ at
  $t \sim 13000 \tau$.
  In other simulations with identical parameters,
  we sometimes observed no hops or two hops between minima,
  as expected with random fluctuating systems.
  In  Fig.~\ref{fig:brownian}(c)
  $T/A_p = 6.0$ 
  we observe approximately 15 hops,
  indicating the random thermalized kicks are
  sufficiently large to make the particle perform
  a random walk of hops a top the substrate
  in addition to the small scale random walk executed
  by all particles in this section.

  A quantity of interest
  for a particle undergoing Brownian motion
  is the rate of displacement
  of the particle from its initial position 
  This is measured as mean square displacement
  as a function of time
  \begin{equation}
    \langle \Delta \vec{r}(t) ^2 \rangle = \langle (\vec{r}(t + t_0) - \vec{r}(t_0))^2\rangle 
  \end{equation}
  where $t_0$ is the initial time at
  initial position $\vec{r}(t_0)$.
  With no substrate, we would expect
  the root mean square displacement (RMSD)
  to be proportional to the elapsed time 
  \begin{equation}
    \sqrt {\langle \Delta \vec{r}(t) ^2 \rangle} \propto t.
  \end{equation}
  Confirm this result for $A_p = 0$.
  Measure the RMSD as a function of time
  of a non-driven colloid for $T/A_p = 0.5, 1.0$, and $2.0$.
  Compare your result to the
  substrate free RMSD.

  %(b)
  How does Brownian motion affect
  the formation of Shapiro steps?
  With driving force reproduce the paper figures...

@@

  A range of interesting behaviors
  can be explored by varying the
  relative strength of the confining landscape
  and external driving force.

%\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
%  \item The Fokker-Planck Equation
%  \item Aubrey-Kontorova + commensurability
%  \item nanotribology
 %   kink motion
 %   Vanossi et al J.Phys.: Condens. Matter 19 (2007)

%\item
  \subsection{Visualizing motion + phase plots}
  \label{ex:animation}

@@

\section{Conclusion}
\label{sec:conclusion}	% You can label sections for reference
A single particle oscillator
in a potential well is 
much like a skateboarder in a half-pipe or
a child on a swing.
If subject to an applied force,
a confined oscillator may 
synchronize its location
to the periodic pattern of the external drive,
moving back and forth in time with
the beat. 
%Fundamental models
%of synchronization 
%can %include many coupled oscillators
%or
%focus on
We have used 
a single particle driven across a periodic potential landscape 
%Single particle studies are useful
to study synchronization dynamics
that arise due to the interplay
between a particles environment and external forces.
%due to interactions between particles.
The relationship between the driving force and
landscape can change the pattern of motion.  
With a constant or 
dc drive the landscape modulates 
the particle velocity, below some threshold  
the dc force is not strong enough to push the particle
across a potential maximum so the average velocity is zero,
a phenomena referred to as pinning \cite{Reichhardt2017}.  
%and dissipating energy from the system at all driving forces.
A sinusoidal or ac drive creates mode-locking,
where the average particle velocity
is fixed for a range of dc drive forces \cite{Reichhardt2015}.

Our simulations reproduce results presented in 
Juniper {\it et al.} \cite{Juniper2015, Juniper2018}
which demonstrated
mode locking in
experiments and simulations of 
driven colloids on a
optical periodic landscape.
Due to the relative ease of
manipulation and imagining, 
colloids are used as experimental models
for systems relatively hard to access and visualize. 
Collections of colloids can
be used to study the properties of solids and liquids
%comprised of smaller particles
%such as atoms \cite{} or electrons \cite{}
or more exotic systems 
such as cold atoms or electron gases \cite{Grier2003}.
%Oscillators ordered into chains or lattices.
%has many important
%technological applications
Dynamical mode-locking, the primary synchronization
effect explored in this paper, 
is %often
observed
in quantum electronic
devices such as Josephson junctions \cite{Josephson1962,Josephson1965}.
A single junction contains 
two superconductoring layers which sandwich an insulating layer.
When subject to an external voltage,
Cooper pairs in the superconducting materials
tunnel through the insulating layer.
Phase-locking is observed as 
%phase-locked current loops \cite{} 
stepped regions in current-voltage (I-V) relationship in these devices,
where voltage is the analog of external driving force
and current is that of particle velocity.
%where a constant current results from a range of voltages
%due to the quantized nature of the tunneling probability [NOT QUITE RIGHT...].
%instead of ohmic relationships.
Known as Shapiro steps, % \cite{},
these phase locked currents  
have been observed due to applied ac voltages in 
single Josephson junctions \cite{Shapiro1963, Golubov2004} and
coupled arrays of junctions \cite{Benz1990}.
%either in 
%velocity-force curves and voltage-current curves \cite{Golubov2004}.
Shapiro steps vary in width depending on the strength of the
applied ac forces,
and are observed in a variety of systems
displaying
%are hallmarks of
non-Ohmic behavior in voltage-current curves,
including
ac and dc driven
charge and spin density waves
and superconducting vortices in landscapes 
engineered with periodic patterns of pinning sites.
Thus the study of
mode-locking is a useful problem
of complex quantum mechanical systems.
Our results can be relevant 
to synchronization effects
in a broad range of experiments systems
including optically confined colloids,
superconductors with periodic pinning arrays, 
and the charge and spin of atomic systems.

>>>>

%In Fig.~\ref{fig:0} 
The driven particle adjusts
its motion to traverse
the periodic landscape with the same rhythm as 
the applied time-dependent force $F^d(t)$.
When $F^d(t) > A_p$, a particle can 
overcome the barrier height of the landscape,
and 
the particle hops between minima in the energy landscape.
%
In Fig.~\ref{fig:0}(a)
we plot $F^d(t)$ %defined in Eq.~\ref{eq:drive}.
as a function of time with
%The time independent
constants $F^{dc}=0.1$, 
$F^{ac}=0.05$ and $f=0.01$ cycles per time unit $\tau$.
The temporal period of the driving force is
$T = 1/f = 100 \tau$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%RAMP
%To avoid transient oscillations at early times, the dc driving force is initially zero and slowly increased %$F^{dc}$. at a rate of $\Delta F^{dc} = 0.01$ every $\Delta t = 4$ time units  to the constant value $F^{dc}=0.1$. In Fig.~\ref{fig:0}(a) we plot $F^{dc}$ in blue to show the increase in  $F^{dc}$ for the first $40$ time units In orange we show  the combined ac and dc drive $F^d(t)$ when the magnitude of the ac applied force is initially zero.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%since $\sin{(0)}=0$.
We mark the maxima of $F^{ac}(t)$
with the
vertical dashed lines %in panels (a) and (b)
-- i.e. $\sin{(\omega t)} = 1$.
%
%
%with the initial driving force at is minimum value 
%$F^d(0) = F^{dc}$. 
%
In Fig.~\ref{fig:0}(b) 
we show the $y-$position of the particle
as a function of time.
We 
normalize $y$ by $\lambda$ %, the spatial period of the potential
to show  particle motion between substrate minima.  
The initial particle position is $y = 0 $. %1 a_0$,
%where the $F^l$ is negative.
%JUST BECAUSE
%causing the particle to move to
%a landscape minima at the start of the simulation.
As the driving force increases,
%the effects of the landscape become less obvious,
the motion of the particle
synchronizes with the driving period $T$.
We measure 
average particle velocity $\langle{v}_y\rangle$
as the average displacement %$\Delta y = y(t_0+T) - y(t_0)$
over the period of the driving force.
The particle moves
in the positive y-direction
through $\Delta y = 2 \lambda$ over the time period $T$,
with 
the average velocity 
$\langle {v}_y \rangle= 2 \lambda f$. % where $T = 1/f$.
The horizontal dashed lines
coincide with the condition the particle is at a substrate minima
where substrate force  $F^l = -A_p$,  
i.e. $\sin{(\pi y / \lambda)} = 1$.
%or $\pi y / \lambda = m \pi/2$, where $m = 1, 5, 7$, {\it etc.}
%Once the particle motion
%coincides with the applied drive,
%indicating synchronization,
The particle synchronizes its motion such that the 
driving force is maximum when the landscape 
force is minimum,
as indicated %with the coincidence of 
with the intersection of
vertical and horizontal lines.  
%i.e. the particle position $y/\lambda$.  
The slope of $y/\lambda$
is proportional to the net force on the particle.
This can be seen in 
Fig.~\ref{fig:0} %we demonstrate this relationship,
where local extrema appear in $y/\lambda$
when $F_{D}(t) \approx 0 $.

@@

  Newton's second law states that
  the acceleration of a particle $i$
  is proportional to 
  the sum of forces on the particle 
  \begin{equation}
  m_i \vec{a}_i = \sum \vec{F}_i
  \label{eq:n2l}
  \end{equation}
  where the constant of proportionality is the
  inertial mass $m_i$.  
  The addition of a dissipative force to a dynamical equation 
  of colloid motion 
  is typically modeled
  with a drag force proportional to the particle's velocity
  in the opposite direction of motion 
  $\vec{F}^{drag} = - \gamma \vec{v}_i$
  where $\gamma = 3 \pi \eta D$ is the drag coefficient
  described in Ex.~\ref{ex:reynolds}.
  The ratio of $m/\gamma$ is %has units of time, % and is 
  known as the momentum relaxation time, %.
  and is small for
  particles with low Reynolds numbers.
  The mass of the
  typical experimental colloid particle is $15$ picograms,
  leading to a momentum relaxation time
  % \tau = 15 nanograms/(3 pi D \eta)
  %$15*10^-12 / (3pi * 3*10^-6 meters * 0.001 Pa-s * 1000 g/kg)$  %1 Pa-s = 1 N s /m^2 = 1 kg /(m s)
  on the order of microseconds.
  %of $1.6 ~\mu$s.
  Confirm for the values listed in Table ~\ref{tab:1},
  the momentum relaxation time is 
  $m/\gamma \approx 0.5 ~\mu$s.

@@

  When solving ordinary differential equations,
  the Euler method is effective for solving linear equations
  of the form
  $dy/dt = f(t,y(t))$ with initial condition $y(t_0) = y_0$.
  The solution is calculated algorithmically
  by stepping in time through $n$ integer steps
  $t_n = t_0 + n \Delta t$.
  At each subsequent step the new
  value for $y$ is calculated as a map solution using
  discrete times 
  $y_{n+1} = y_n + f(t_n,y_n)$.
  The Euler method can be applied to non-linear
  equations effectively if the time step $\Delta t$
  is kept sufficiently small \cite{Newman}.
  In our simulations we use the timestep $\Delta t = 0.001$,
  but we find for a single particle
  we can just as easily used 
  %examine 
  %for
  timesteps $\Delta t = 0.01$ and $\Delta t = 0.1$
  over the same maximum time
  (i.e. decrease the overall simulation time and sampling rate)
  and reproduce the motions shown in Fig.~\ref{fig:0}(b).
  This is due to the linear nature of the solution
  for an isolated particle.
  Apply the Euler method to our equation
  of motion to solve for the analytic expression
  of position of a particle
  $y_n$ at the $nth$ timestep (i.e. Eq.~\ref{eq:euler}).
  %How to the motions of the particle compare when the timestep
  %becomes large?
  [UPDATE]
  Demonstrate the timestep
  of a single particle can be made large
  with no change to the overall physics.
  You will need to modify the maximum
  simulation time, and the frequency of data saved for plotting purposes.

  Interaction with neighboring particles
  makes a small timestep essential for molecular dynamics simulations.
  Since particle-particle interactions are typically non-linear,
  the interaction force changes significantly over small distances,
  making this simulation a unique
  exception to typical simulation timesteps.
  %{\it small timesteps matter a great deal when particle interactions
  %  are included in the model.  I have demonstrated that
  %  without particle interactions we can increase the timestep
  %with no penalty, so this isn't a very interesting problem.}
  %FOLLOW UP WITH THIS!
  %Because we are performing molecular dynamics
  %for a single particle on a smooth potential energy landscape,
  %we use a large simulation time step of 
  %$\Delta t = 0.01$.  %In Sec.~\ref{sec:sync},
  %we decrease the time step
  %to treat multiple particle interactions.

@@

  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{brownian_particle_dt0.1}.pdf}
      \caption{
        Motion of a particle undergoing Brownian motion
        on a washboard potential
        energy landscape.
        (a) $T/A_p = 4.0$ no hopping occurs.
        (b) $T/A_p = 5.0$ a single hop occurs at $t = 130000$
        (c) $T/A_p = 6.0$ many hops occur.
        Note the scale of the $y-$axis differs in each panel.
      }
      \label{fig:brownian}
    \end{figure}
  \end{center}
  In Fig.~\ref{fig:brownian}
  we show the position versus time of a particle
  confined to a sinusoidal landscape
  undergoing Brownian motion.
  We increase the temperature relative
  to the amplitude of the landscape
  troughs until the particle enters a hopping regime.
  In  Fig.~\ref{fig:brownian}(a)
  $T/A_p = 4.0$ and the particle executes a 
  random walk centered at the potential minima $y/\lambda = 10$.
  We ran many simulations and never observed a hop to another minima.
  In  Fig.~\ref{fig:brownian}(b)
  $T/A_p = 5.0$ where hops between
  potential minima are possible but not probable,
  a single hop occurs from
  $y/\lambda = 10$ to $y/\lambda = 11$ at
  $t \sim 13000 \tau$.
  In other simulations with identical parameters,
  we sometimes observed no hops or two hops between minima,
  as expected with random fluctuating systems.
  In  Fig.~\ref{fig:brownian}(c)
  $T/A_p = 6.0$ 
  we observe approximately 15 hops,
  indicating the random thermalized kicks are
  sufficiently large to make the particle perform
  a random walk of hops a top the substrate
  in addition to the small scale random walk executed
  by all particles in this section.

  A quantity of interest
  for a particle undergoing Brownian motion
  is the rate of displacement
  of the particle from its initial position 
  This is measured as mean square displacement
  as a function of time
  \begin{equation}
    \langle \Delta \vec{r}(t) ^2 \rangle = \langle (\vec{r}(t + t_0) - \vec{r}(t_0))^2\rangle 
  \end{equation}
  where $t_0$ is the initial time at
  initial position $\vec{r}(t_0)$.
  With no substrate, we would expect
  the root mean square displacement (RMSD)
  to be proportional to the elapsed time 
  \begin{equation}
    \sqrt {\langle \Delta \vec{r}(t) ^2 \rangle} \propto t.
  \end{equation}
  Confirm this result for $A_p = 0$.
  %[INSERT advice on length of time to run?]
  Measure the RMSD as a function of time
  of a non-driven colloid for $T/A_p = 4.0, 5.0$, and $6.0$,
  as shown in Fig.~\ref{fig:brownian}.
  Compare your result to the
  substrate free RMSD.
  %%[INSERT EXPECTED RESULTS.  presumbably for sufficiently large $T/A_p$ the result collapsed back to standard diffusion.]

  %(b)
  How does Brownian motion affect
  the formation of Shapiro steps?
  With driving force reproduce the paper figures...
  %%[there is no way I want to run this with python...]

@@

  A range of oscillation behaviors
  can be explored by varying the
  relative strength of the confining landscape
  and external driving force.
  For the single driven particle,
  the hopping patterns are typically characterized
  by $n_f$ the number of steps forward
  versus $n_b$ the number of steps backward within a single
  time period.
  The total displacement of $n_f - n_b$ integer steps of
  the substrate period $\lambda$ characterize
  the net hop length.  
  In Fig.~\ref{fig:0},
  in a single period 
  the particle moves forward through two minima, i.e. $n_f = 2$,
  and does not move backward a full minima ($n_b = 0$).  
  %such that the pattern
  %is characterized as $2(2,0)$.
  In order to achieve
  backwards hops,
  a particle must have a ratio of $F^{ac}/F^{dc} > 1$,
  and a difference $|F^{ac} - F^{dc}| > A_p$.
  %which can also produce large forward hops.
  %INSERT figure with a range of hopping patterns for a run
  The frequency must be sufficiently low so that
  the time interval in which the applied force is large
  is sustained so that a particle will
  traverse a substrate extrema.
  Experiments with single colloids \cite{Juniper2015} 
  show 
  hopping patterns with backward steps are more difficult
  to achieve than forward,
  with $n_f = 0$ to $6$ for $n_b = 0$,
  $n_f = 0$ to $5$ for $n_b = -1$,
  and
  $n_f = 2$ to $3$ for $n_b = -2$
  were realized 
  for a variety of applied forces parameters $F^{dc}$ and $F^{ac}$.

  In Fig.~\ref{fig:hops}
  we show the results for lowering the frequency
  of the system for our original parameters.
  For the parameters
  $F^{dc}=0.1$, $F^{ac}=0.05$, and $a_p = 0.1$,
  $n_b = 0$
  across a broad range of frequencies,
  and $n_f$ increases as frequency decreases.
  Low frequencies
  result in sustained positive or negative motion of a particle,
  where in Fig.~\ref{fig:hops}(e)
  the particle reaches the top edge of the system
  and wraps back to $y=0$.

  In Fig.~\ref{fig:hops_back}
  we show the results for increasing $F^{ac}$
  of the system for our original parameters.
  Here $n_b$ increases from $n_b = 0$ in (a) to

  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{parameters_fig5}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc} = 0.1$ and $F^{ac} = 0.05$ as Fig.~\ref{fig:1} and decreasing frequency as marked.    
      }
      \label{fig:hops}
    \end{figure}
  \end{center}
  %In Fig.~\ref{fig:hops}

  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{parameters_fig6}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:1} and increasing $F^{ac}$.
        (a) The particle moves forward six minima with no steps backward.
        (b) The particle moves forward eight minima with two steps backward.
        (c) The particle moves forward nine minima with four steps backward.
      }
      \label{fig:hops_back}
    \end{figure}
  \end{center}
  %In Fig.~\ref{fig:hops}

%\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
%  \item The Fokker-Planck Equation
%  \item Aubrey-Kontorova + commensurability
%  \item nanotribology
 %   kink motion
 %   Vanossi et al J.Phys.: Condens. Matter 19 (2007)
  %\item

  \subsection{Visualizing motion + phase plots}
  \label{ex:animation}

@@

\section{Conclusion}
\label{sec:conclusion}	% You can label sections for reference
A single particle oscillator
in a potential well is 
like a skateboarder in a half-pipe or
a child on a swing.
%If subject to an applied force,
A confined oscillator may 
synchronize its location
to the periodic pattern of the external drive,
moving back and forth in time with
the beat. 
The relationship between the driving force and
landscape can change the pattern of motion.  
With a constant or 
dc drive the landscape modulates 
the particle velocity, below some threshold  
the dc force is not strong enough to push the particle
across a potential maximum so the average velocity is zero,
a phenomena referred to as pinning \cite{Reichhardt2017}.
Above the pinning threshold,
a particle subject to a constant
drive force will increase its speed at a rate propotional
to the external drive.  
%and dissipating energy from the system at all driving forces.
A sinusoidal or ac drive can create mode-locking,
where the average particle velocity
is fixed for a range of dc drive forces \cite{Reichhardt2015}.
This synchronization phenomena
is useful for understanding the complex dynamical 
systems.

%Fundamental models
%of synchronization 
%can %include many coupled oscillators
%or
%focus on
We have used 
a single particle driven across a periodic potential landscape 
%Single particle studies are useful
to study synchronization dynamics
that arise due to the interplay
between environmental and external forces.
%due to interactions between particles.
Our simulations reproduce results presented in 
Juniper {\it et al.} \cite{Juniper2015} %, Juniper2018}
which demonstrate 
mode locking in
experiments and simulations of 
driven colloids on a
periodic optical landscape.
Due to the relative ease of
manipulation and imagining, 
colloids are used as experimental models
for systems %relatively
hard to access and visualize 
such as cold atoms or electron gases \cite{Grier2003}.
%Collections of colloids can
%be used to study the properties of solids and liquids
%or more exotic systems 
%Oscillators ordered into chains or lattices.
%has many important
%technological applications
Dynamical mode-locking, the primary synchronization
effect explored in this paper, 
is %often
observed
in quantum electronic
devices such as Josephson junctions \cite{Josephson1962,Josephson1965}.
%A single junction contains 
%two superconductoring layers which sandwich an insulating layer.
%When subject to an external voltage,
%Cooper pairs in the superconducting materials
%tunnel through the insulating layer.
Phase-locking is observed as 
stepped regions in current-voltage (I-V) relationship in these devices,
where voltage is the analog of external driving force
and current is that of particle velocity.
Known as Shapiro steps, % \cite{},
these phase locked currents  
have been observed due to applied ac voltages in 
single Josephson junctions \cite{Shapiro1963, Golubov2004} and
coupled arrays of junctions \cite{Benz1990}.
Shapiro steps vary in width depending on the strength of the
applied ac forces,
and are observed in a variety of systems
displaying
%are hallmarks of
non-Ohmic behavior in voltage-current curves,
including
ac and dc driven
charge and spin density waves
and superconducting vortices in landscapes 
engineered with periodic patterns of pinning sites.
Thus the study of
mode-locking is a useful probe 
of complex quantum mechanical systems.
Our results can be relevant 
to synchronization effects
in a broad range of experiments systems
including optically confined colloids,
superconductors with periodic pinning arrays, 
and the charge and spin of atomic systems.
